Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
fix coercion resistance crap

Coercion resistance means that secrecy is maintained even if interaction
with the coercer is allowed throughout the voting process.
The distinction between receipt-freeness and coercion resistance is subtle,
and is commonly often lost in ambiguity due to a lack of formal definitions. \cite{delaune}
In some verifiable voting systems, receipt-freeness directly implies coercion resistance,
but this is not necessarily the case.

Even in a receipt-free system,
if the voting process involves a multi-step iteraction involving the coercer,
it may be possible for the voter to prove to the coercer that she is following
some protocol. \cite{delaune}
A simple example that is common to many proposed voting systems is
the \term{Italian attack}. \cite{preta}
This problem arises when the ballot contains a large number of voting options,
such as a ranked election in which the number of possibilities grows as the
factorial of the number of candidates.
If the voter and coercer have one interaction prior to voting,
they can follow this protocol:
\begin{enumerate}
\item A coercer who favors candidate $c_1$ randomly permutes $[2, n]$ and
communicates the resulting permutation $\pi$ to the voter.
\item The voter casts a ballot ranking candidates in the order
$c_1, c_{\pi(2)}, c_{\pi(3)}, \ldots$.
\item The coercer, seeing the resulting ballot in the published list of votes,
is assured that it was cast by the voter with probability
$\ge 1 - \frac{1}{(n-1)!}$.
\end{enumerate}

>>>>

Coercion resistance means that secrecy is maintained even if interaction
with the coercer is allowed throughout the voting process.
The distinction between receipt-freeness and coercion resistance is subtle,
and is commonly often lost in ambiguity due to a lack of formal definitions \cite{delaune}.
In some verifiable voting systems, receipt-freeness directly implies coercion resistance,
but this is not necessarily the case.

Even in a receipt-free system,
if the voting process involves a multi-step iteraction involving the coercer,
it may be possible for the voter to prove to the coercer that she is following
some protocol \cite{delaune}.
A simple example that is common to many proposed voting systems is
the \term{Italian attack} \cite{preta}.
This problem arises when the ballot contains a large number of voting options,
such as a ranked election in which the number of possibilities grows as the
factorial of the number of candidates.
If the voter and coercer have one interaction prior to voting,
they can follow this protocol:
\begin{enumerate}
\item A coercer who favors candidate $c_1$ randomly permutes $[2, n]$ and
communicates the resulting permutation $\pi$ to the voter.
\item The voter casts a ballot ranking candidates in the order
$c_1, c_{\pi(2)}, c_{\pi(3)}, \ldots$.
\item The coercer, seeing the resulting ballot in the published list of votes,
is assured that it was cast by the voter with probability
$\ge 1 - \frac{v}{(n-1)!}$, where $v$ is the number of voters.
\end{enumerate}
